\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[letterpaper,margin=0.75in]{geometry}
\usepackage{setspace}

\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.7in}
\addtolength{\textheight}{10.25in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-4pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\setstretch{1.0}

\begin{center}
    \textbf{\Huge \scshape Shriyansh Singh} \\ \vspace{1pt}
    \small \textbf{+1 930 333 5141}  $|$ \href{mailto:shriyansh.singh24@gmail.com}{\textbf{\underline{shriyansh.singh24@gmail.com}}} $|$ 
    \href{https://www.linkedin.com/in/shriyansh-bir-singh}{\textbf{\underline{linkedin.com/in/shriyansh-bir-singh}}}
\end{center}

\vspace{-25pt}
%--------------Objective
\section{\textbf{SUMMARY}}
      {Machine Learning Engineer with expertise in building and deploying ML models and data pipelines using Python, TensorFlow, Spark, and AWS. Proven ability to drive business impact through scalable, cloud-based solutions and automation. Passionate about optimizing the entire ML lifecycle to deliver high-performance, reliable outcomes.}
\vspace{-10pt}

%-----------EXPERIENCE-----------
\section{\textbf{PROFESSIONAL EXPERIENCE}}
\vspace{-1pt}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Machine Learning Intern}{\textit{Apr 2024 -- Present}}
      {\textbf{Hyphenova AI}}{Los Angeles, California}
      \resumeItemListStart
        \resumeItem{Developed and deployed NLP models using Python and TensorFlow to filter content with 30\% higher accuracy, directly increasing user satisfaction by 15\% through Agile-based iteration and feedback loops.}
        \resumeItem{Built and automated ML pipelines with Apache Spark and AWS (S3, Glue), cutting data processing time by 40\% and facilitating real-time model deployment and monitoring.}
        \resumeItem{Improved predictive accuracy of models by 25\% using advanced feature engineering and optimization of Random Forest and deep learning algorithms, enhancing brand-creator matching.}
        \resumeItem{Streamlined data preprocessing and feature selection to enhance training efficiency, achieving 15\% better accuracy for underrepresented categories by applying SMOTE and custom resampling methods.}
        \resumeItem{Converted data science prototypes into production models using AWS SageMaker and Lambda, implementing CI/CD pipelines to automate deployment and governance processes.}
        \resumeItem{Established model monitoring and governance using real-time validation scripts, boosting data reliability by 30\% and reducing errors by 20\%, ensuring consistent model performance.}
        \resumeItem{Managed the full ML lifecycle, including data collection, preprocessing, deployment, and monitoring using AWS and Python, ensuring scalable and reliable ML operations.}
        \resumeItem{Implemented advanced ML algorithms, such as deep neural networks and LLMs, to tackle complex datasets and enhance decision-making accuracy.}
        \resumeItem{Automated ML deployment workflows on AWS using CI/CD pipelines and Terraform, cutting deployment time and minimizing manual errors.}
      \resumeItemListEnd

    \resumeSubheading
      {Data Analyst Intern}{\textit{May 2022 -- Oct 2022}}
      {\textbf{Enterprise Business Technologies Pvt. Ltd}}{Mumbai, India}
      \resumeItemListStart
        \resumeItem{Analyzed large datasets using SQL and Python to drive business strategies, increasing project completion rates by 25\% and client satisfaction by 20\%.}
        \resumeItem{Optimized data models and automated reports in Power BI, boosting data accuracy by 15\% and cutting report generation time by 40\%, facilitating quicker decision-making.}
        \resumeItem{Built predictive models using regression analysis in Python, improving forecast accuracy by 18\% and driving a 10\% increase in quarterly revenue.}
        \resumeItem{Collaborated with cross-functional teams to embed data analytics into decision-making, advancing data-driven business strategies and project outcomes.}
        \resumeItem{Created automated data validation pipelines in Python, enhancing data integrity across reporting systems and reducing manual errors by 20\%.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{\textbf{EDUCATION}}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Indiana University Bloomington}{Indiana, United States}
      {\textbf{Master of Science in Data Science}}{Aug 2023 -- May 2025}
  \resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{\textbf{SKILLS}}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming Languages}{: Python, Java, C++, Scala} \\
     \textbf{Machine Learning Frameworks}{: TensorFlow, PyTorch, Scikit-learn, XGBoost, Keras} \\
     \textbf{Data Engineering and Big Data}{: Apache Spark, Hadoop, AWS (S3, EC2, Glue, Lambda, SageMaker), Databricks, Kafka, Airflow, Terraform} \\
     \textbf{Cloud and Automation}{: AWS (SageMaker, Lambda, Glue), Azure, GCP, Docker, Kubernetes, CI/CD Pipelines, Infrastructure as Code (Terraform)} \\
     \textbf{NLP and Deep Learning}{: NLP Techniques, LLMs, Transformers, Hugging Face} \\
     \textbf{Data Analysis and Visualization}{: Pandas, NumPy, Power BI, Tableau, D3.js} \\
     \textbf{Databases}{: \textbf{SQL} (MySQL, PostgreSQL, Microsoft SQL Server), \textbf{NoSQL} (MongoDB, Cassandra, Neo4j)} \\
     \textbf{Development Tools}{: Git, Bash, Jupyter Notebooks, VS Code, IntelliJ} \\
    }}
 \end{itemize}

%-----------PROJECTS-----------
\section{\textbf{PROJECTS}}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{NLP-Based Content Filtering System} $|$ \emph{Python, TensorFlow, NLP, AWS}}{\textit{Nov 2023 -- Dec 2023}}
          \resumeItemListStart
            \resumeItem{Enhanced text classification and entity recognition with LLMs and pre-trained embeddings, improving filtering accuracy of inappropriate content by 40\%}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

\end{document}