\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[letterpaper,margin=0.75in]{geometry}
\usepackage{setspace}

\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.7in}
\addtolength{\textheight}{10.25in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure ATS parsable PDF
\pdfgentounicode=1

\begin{document}
\setstretch{1.0}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Shriyansh Singh} \\ \vspace{1pt}
    \small \textbf{+1-930-333-5141}  $|$ \href{mailto:shriyansh.singh24@gmail.com}{\textbf{\underline{shriyansh.singh24@gmail.com}}} $|$ 
    \href{https://www.linkedin.com/in/shriyansh-bir-singh}{\textbf{\underline{LinkedIn}}} 
\end{center}

%----------SUMMARY----------
\section{\textbf{SUMMARY}}
Results-driven Data Scientist with expertise in predictive modeling, data engineering, and machine learning. Adept at transforming raw data into actionable insights, optimizing business strategies through analytics, and deploying scalable AI solutions. Passionate about innovation, cross-functional collaboration, and enhancing data-driven decision-making.

%-----------PROFESSIONAL EXPERIENCE-----------
\section{\textbf{PROFESSIONAL EXPERIENCE}}
  \begin{itemize}[leftmargin=0.15in, label={}]

    \item \textbf{Data Science Intern} \hfill \textit{April 2024 – Present} \\
    \textbf{Hyphenova AI}, Los Angeles, CA
    \begin{itemize}
        \item Performed exploratory data analysis (EDA), feature engineering, and data cleansing using Python (Pandas, NumPy) and SQL, reducing data ambiguity by 35\% and improving predictive accuracy.
        \item Developed and optimized machine learning models (logistic regression, ensemble methods) that improved key business forecast accuracy by 20\%.
        \item Automated data preprocessing and feature engineering workflows, reducing manual effort by 40\% and ensuring high data integrity.
        \item Designed and deployed interactive Power BI dashboards to visualize KPIs, enhancing decision-making speed by 30\% for executive leadership.
    \end{itemize}

    \item \textbf{Data Science Intern} \hfill \textit{Feb 2023 – May 2024} \\
    \textbf{Enterprise Business Technologies Pvt. Ltd}, Mumbai, India
    \begin{itemize}
        \item Analyzed multi-terabyte datasets using SQL and Python, extracting key insights that improved business efficiency by 15\%.
        \item Built and fine-tuned machine learning models (Random Forest, Gradient Boosting) for churn prediction, achieving an 18\% boost in AUC scores.
        \item Implemented A/B testing and statistical hypothesis testing to validate business strategies, leading to a 12\% increase in customer retention.
        \item Developed and maintained Tableau dashboards, reducing manual reporting time by 40\% and increasing stakeholder engagement.
    \end{itemize}
  \end{itemize}

%-----------PROJECTS-----------
\section{\textbf{PROJECTS}}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \item \textbf{Predictive Customer Churn Model} \hfill Python, XGBoost, Tableau | \textit{Nov 2023 – Feb 2024}
    \begin{itemize}
        \item Developed an ensemble-based churn prediction model, improving AUC by 18\% over baseline models.
        \item Implemented recursive feature elimination and correlation analysis, reducing model error by 15\%.
        \item Created interactive Tableau dashboards for real-time churn monitoring, optimizing customer retention strategies.
    \end{itemize}
    
    \item \textbf{Interactive Sales Forecasting Dashboard} \hfill Python, ARIMA, LSTM, Power BI | \textit{Jul 2023 – Oct 2023}
    \begin{itemize}
        \item Built a hybrid time-series forecasting model (ARIMA + LSTM), increasing forecast accuracy by 18\% on historical sales data.
        \item Automated data extraction and transformation workflows, reducing processing time by 40\%.
        \item Designed an interactive Power BI dashboard for real-time trend visualization, improving strategic decision-making speed by 30\%.
    \end{itemize}
  \end{itemize}

%-----------TECHNICAL SKILLS-----------
\section{\textbf{TECHNICAL SKILLS}}
\begin{itemize}[leftmargin=0.15in, label={}]
    \item \textbf{Programming:} Python, SQL, R, Java
    \item \textbf{Data Science \\ ML:} Scikit-learn, TensorFlow, PyTorch, XGBoost, Keras
    \item \textbf{Big Data \\ Cloud:} Apache Spark, Hadoop, AWS (S3, Redshift, EC2), Azure, GCP (BigQuery)
    \item \textbf{Data Visualization:} Power BI, Tableau, Matplotlib, Seaborn
    \item \textbf{DevOps \\ MLOps:} Docker, Git, CI/CD Pipelines, Kubernetes
    \item \textbf{Soft Skills:} Problem-Solving, Critical Thinking, Communication, Leadership
\end{itemize}

%-----------EDUCATION-----------
\section{\textbf{EDUCATION}}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \item \textbf{Indiana University Bloomington} \hfill \textit{Aug 2023 -- May 2025} \\
    Master of Science in Data Science, Indiana, United States
    \begin{itemize}
        \item Relevant Coursework: Data Visualization, Big Data Applications, Cloud Computing, Graph Analytics, Applied ML, Deep Learning
    \end{itemize}
  \end{itemize}

\end{document}
