\documentclass[12pt,a4paper]{article}
\usepackage[left=0.75cm,right=0.75cm,top=1cm,bottom=1cm]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fontawesome}
\usepackage{array}
\usepackage{times}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.3em}

% Adjust section formatting
\titleformat{\section}{\normalsize\bfseries}{\thesection}{1em}{}[\titlerule]
\titlespacing*{\section}{0pt}{0.25em}{0.25em}
\titleformat{\subsection}{\normalsize\bfseries}{\thesubsection}{1em}{}
\titlespacing*{\subsection}{0pt}{0.25em}{0.1em}

\begin{document}

%-------------------------------------------
% Header & Contact Info
%-------------------------------------------
\begin{center}
  {\Large \textbf{SHRIYANSH SINGH}}\\[0.5em]
  +1 930 333 5141 $\cdot$ \href{mailto:shriyansh.singh24@gmail.com}{shriyansh.singh24@gmail.com} $\cdot$ 
  \href{https://www.linkedin.com/in/shriyansh-bir-singh}{LinkedIn} $\cdot$ 
  \href{https://github.com/shriyansh24}{GitHub}\\[0.5em]
  % Consider adding a personal website if available.
\end{center}

%-------------------------------------------
% Education
%-------------------------------------------
\section*{EDUCATION}
\textbf{Indiana University Bloomington} \hfill Aug 2023 -- May 2025\\
Master of Science in Data Science, Indiana, USA\\[0.3em]
\textbf{Relevant Courses:} Applied Machine Learning, Intelligent Systems, Data Mining, Big Data Applications, Cloud Computing, Graph Analytics, Information Visualization, Applied Database Technologies

%-------------------------------------------
% Professional Experience
%-------------------------------------------
\section*{PROFESSIONAL EXPERIENCE}

\textbf{Machine Learning Engineer Intern -- Cloud AI Solutions} \hfill Jun 2023 -- Present\\
San Francisco, CA
\begin{itemize}[leftmargin=*,noitemsep,topsep=0pt]
  \item Developed and deployed end-to-end machine learning pipelines for financial risk modeling, reducing model inference time by 35\% and improving prediction accuracy by 20\%.
  \item Engineered scalable data ingestion and preprocessing workflows using Apache Spark and AWS Lambda, processing over 500K transactions daily.
  \item Optimized deep learning models using TensorFlow and PyTorch; implemented distributed training and hyperparameter tuning to cut training time by 30\%.
  \item Collaborated with cross-functional teams to integrate ML models into production systems, achieving a 40\% boost in system throughput and lowering latency in real-time applications.
\end{itemize}

\textbf{Research Assistant in Machine Learning -- Data-Driven Healthcare} \hfill Aug 2022 -- May 2023\\
Indiana University, Bloomington, IN
\begin{itemize}[leftmargin=*,noitemsep,topsep=0pt]
  \item Designed and implemented a convolutional neural network for medical image segmentation, increasing the dice coefficient from 0.78 to 0.85.
  \item Leveraged transfer learning with ResNet and U-Net to detect anomalies in radiology images, reducing false positive rates by 25\%.
  \item Automated continuous integration and model monitoring using Docker and Kubernetes, ensuring 99.5\% uptime in a production-like environment.
  \item Authored technical reports and collaborated on publications; enhanced model interpretability using SHAP and LIME for clinical decision support.
\end{itemize}

%-------------------------------------------
% Projects
%-------------------------------------------
\section*{PROJECTS}

\textbf{Real-Time Stock Market Anomaly Detection} \hfill \textit{Personal Project}\\
\begin{itemize}[leftmargin=*,noitemsep,topsep=0pt]
  \item Developed an LSTM-based anomaly detection system for real-time financial data, reducing false alerts by 30\% and enabling proactive risk management.
  \item Integrated statistical techniques with deep learning to flag abnormal market behaviors and deployed the model on AWS SageMaker for scalability.
  \item Implemented automated data pipelines to process streaming data from multiple financial sources.
\end{itemize}

\textbf{Medical Image Analysis for Disease Detection} \hfill \textit{Personal Project}\\
\begin{itemize}[leftmargin=*,noitemsep,topsep=0pt]
  \item Built an advanced CNN-based system to detect diabetic retinopathy from retinal images, achieving 92\% accuracy on a benchmark dataset.
  \item Utilized data augmentation and transfer learning to overcome limited data challenges; integrated model monitoring using TensorFlow Serving and Kubernetes.
  \item Developed an end-to-end pipeline from image preprocessing to real-time prediction, enabling timely clinical decision support.
\end{itemize}

\textbf{E-commerce Product Recommendation System} \hfill \textit{Personal Project}\\
\begin{itemize}[leftmargin=*,noitemsep,topsep=0pt]
  \item Engineered a hybrid recommendation engine that combined collaborative filtering with deep learning, resulting in a 25\% increase in click-through rates.
  \item Leveraged Apache Spark for large-scale data processing and deployed the model on Azure ML to support real-time personalized recommendations.
  \item Conducted A/B testing to validate model performance and continuously optimized the system based on user feedback.
\end{itemize}

\textbf{LLM-Powered Customer Support Chatbot} \hfill \textit{Personal Project}\\
\begin{itemize}[leftmargin=*,noitemsep,topsep=0pt]
  \item Fine-tuned a large language model using Hugging Face Transformers to create an intelligent chatbot for an e-commerce platform, achieving an 85\% first-contact resolution rate.
  \item Integrated the chatbot with a real-time API on Google Cloud AI Platform, reducing average customer handling time by 40\%.
  \item Employed advanced NLP techniques to understand and generate human-like responses, ensuring high customer satisfaction.
\end{itemize}

%-------------------------------------------
% Skills
%-------------------------------------------
\section*{SKILLS}

\textbf{Machine Learning \& Deep Learning:} TensorFlow, PyTorch, Keras, Scikit-Learn, Hugging Face Transformers, U-Net, ResNet, LSTM, CNN, RNN, Graph Neural Networks\\[0.3em]
\textbf{Programming \& Data Processing:} Python, R, SQL, Pandas, NumPy, Apache Spark, Hadoop, Dask\\[0.3em]
\textbf{Cloud Platforms \& Deployment:} AWS SageMaker, Google Cloud AI Platform, Azure ML, Docker, Kubernetes, Terraform\\[0.3em]
\textbf{MLOps \& DevOps:} MLflow, Apache Airflow, Jenkins, Git, GitHub, CI/CD Pipelines\\[0.3em]
\textbf{Specializations:} Natural Language Processing (NLP), Computer Vision, Time Series Forecasting, Model Interpretability (SHAP, LIME), Real-Time Analytics, Anomaly Detection, Recommendation Systems

\end{document}
