
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[letterpaper,margin=0.75in]{geometry}
\usepackage{setspace}

\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.7in}
\addtolength{\textheight}{10.25in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated pdf is machine-readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-4pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\setstretch{1.0}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Shriyansh Singh} \\ \vspace{1pt}
    \small \textbf{+1-930-333-5141}  $|$ \href{mailto:shriyansh.singh24@gmail.com}{\textbf{\underline{shriyansh.singh24@gmail.com}}} $|$ 
    \href{https://www.linkedin.com/in/shriyansh-bir-singh}{\textbf{\underline{LinkedIn}}} 
\end{center}

%----------SUMMARY----------
\section{\textbf{SUMMARY}}
Machine Learning Engineer skilled in Python, medical image analysis, deep learning, and computer vision; passionate about developing AI-based decision support tools for precision cancer diagnosis.

%-----------PROFESSIONAL EXPERIENCE-----------
\section{\textbf{PROFESSIONAL EXPERIENCE}}
  \resumeSubHeadingListStart
  
    \resumeSubheading
      {Machine Learning Engineer Intern}{\textit{April 2024 - Dec 2024}}
      {\textbf{Hyphenova AI}}{Los Angeles, CA}
      \resumeItemListStart
        \resumeItem{Trained DSSM and CNN-based TensorFlow models to classify intent from queries; methods applicable to histopathology image interpretation and multimodal correlation tasks.}
        \resumeItem{Developed scalable Apache Spark and Kafka pipelines that processed 5TB of logs daily, aligning with multimodal medical imaging workflows.}
        \resumeItem{Reduced latency by 30\% via TensorFlow model optimization, enabling deployment of real-time clinical decision support tools.}
        \resumeItem{Deployed models using Docker, Kubernetes, and AWS Sagemaker with 99.9\% uptime; suitable for federated learning architectures.}
        \resumeItem{Collaborated with data scientists and clinicians to map model predictions to patient-centric performance metrics.}
      \resumeItemListEnd

    \resumeSubheading
      {Machine Learning Engineer Intern}{\textit{Feb 2023 - May 2024}}
      {\textbf{Enterprise Business Technologies Pvt Ltd}}{Mumbai, India}
      \resumeItemListStart
        \resumeItem{Built ensemble models for prediction using large-scale tabular datasets, analogous to integrating radiomic and genomic features for cancer risk stratification.}
        \resumeItem{Engineered robust feature pipelines in Python and SQL, cutting preprocessing time by 50\%; directly applicable to healthcare record harmonization.}
        \resumeItem{Implemented Docker-based model monitoring tools, reducing anomaly detection time from 5 days to 3 hours.}
        \resumeItem{Integrated user behavior streams via PySpark, simulating multimodal signal integration from clinical and imaging sources.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{\textbf{PROJECTS}}
  \resumeSubHeadingListStart
  
    \resumeProjectHeading
        {\textbf{Dynamic Ranking with Deep \& Wide + DSSM Models} $|$ \emph{Python, TensorFlow, AWS}}{\textit{Nov 2023 – Feb 2024}}
        \resumeItemListStart
          \resumeItem{Built a recommender using DSSM and Deep \& Wide models, conceptually similar to combining imaging and demographic inputs for clinical predictions.}
          \resumeItem{Deployed Airflow-based retraining on AWS; ensured robust, reproducible ML lifecycle management aligned with medical AI deployment standards.}
        \resumeItemListEnd
        
    \resumeProjectHeading
        {\textbf{Segmentation via Embeddings \& Transfer Learning} $|$ \emph{MXNet, SQL, Tableau}}{\textit{Jul 2023 – Oct 2023}}
        \resumeItemListStart
          \resumeItem{Designed unsupervised clustering on deep embeddings to discover user segments; technique transferrable to spatial omics-driven phenotyping.}
          \resumeItem{Visualized pipeline results in Tableau, fostering interpretability of deep models—crucial in clinical validation environments.}
        \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------SKILLS & CERTIFICATIONS-----------
\section{\textbf{SKILLS \& CERTIFICATIONS}}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming:}{ Python, C++, Shell, SQL, Jupyter} \\
     \textbf{Medical Imaging \& CV:}{ OpenCV, Scikit-image, TensorFlow/Keras} \\
     \textbf{ML/DL Frameworks:}{ TensorFlow, PyTorch, Scikit-learn, MXNet} \\
     \textbf{Deployment/Cloud:}{ Docker, Kubernetes, AWS (S3, EC2, SageMaker), GCP} \\
     \textbf{Data Engineering:}{ Apache Spark, Kafka, Hadoop, SQL} \\
     \textbf{Visualization:}{ Tableau, Power BI, Plotly}
    }}
 \end{itemize}

%-----------EDUCATION-----------
\section{\textbf{EDUCATION}}
  \resumeSubHeadingListStart
  
    \resumeSubheading
      {Indiana University Bloomington}{\hfill Aug 2023 -- May 2025}
      {\textbf{Master of Science in Data Science}}{Indiana, United States}
      \resumeItemListStart
        \resumeItem{Relevant Coursework: Deep Learning, Computer Vision, Machine Learning, Cloud Computing, Big Data Applications, Graph Analytics}
      \resumeItemListEnd
    
  \resumeSubHeadingListEnd

\end{document}
